Cover letter for the original IJRR submission

### 2017-10-02 body/appendix_optim.tex
andrea s comments

\begin{equation} \label{eq:qp_rob} \begin{aligned}
%~ \find \quad & \mx{R} \in \Rv{3\times T}, \mxdd{C} \in  \Rv{6\times T} \\
\minimize_{\mathbf{c}(t), \mathbf{\dot{c}}(t), \mathbf{\ddot{c}}(t), \mathbf{w}(t)}  \quad & \sum_{u=0}^{2} \int_{t_u}^{t_u + \Delta t_u}  \ell(\mathbf{c}(t), \mathbf{\dot{c}}(t), \mathbf{\ddot{c}}(t), \mathbf{w}(t)) \text{dt}  \\
\st \quad & \mathbf{\ddot{c}}(t) = dyn(\mathbf{c}(t), \mathbf{\dot{c}}(t), \mathbf{w}(t)) \\
	\quad & \mathbf{A}_u \mathbf{w}(t)  \leq \mathbf{b}_u , \forall t \in  \left[t_u, t_u + \Delta t_u \right[, \forall u \\
	\quad & \mathbf{Y}_u \mathbf{c}(t)  \leq \mathbf{y}_u , \forall t \in  \left[t_u, t_u + \Delta t_u \right[, \forall u \\
	\quad & \mathbf{c}(0)  = \mathbf{c}_{\mathbf{q}_0} \\
	\quad & \mathbf{c}(T)  = \mathbf{c}_{\mathbf{q}_1} \\
	\quad & \mathbf{c}(0)  = \mathbf{\dot{c}}(0)  = \mathbf{\ddot{c}}(0) = \mathbf{0}\\
	\quad & \mathbf{c}(T)  = \mathbf{\dot{c}}(T)  = \mathbf{\ddot{c}}(T) = \mathbf{0}\\
    %~ \quad & ({\vct{r}}\tra\vct{r}=1,  \forall t  ?) \\
    %~ \quad & \delta t \sum\limits_1^{T-1}{\vc{r}^1}\tra {\vc{r}^1} \ge t_{transit} \\
    %~ \quad & \mx{A}_{\int} \mxdd{C} \leq \vc{a}_{\int} \\
    %~ \quad & \mx{V}_{\int} \mxd{C} \leq \vc{v}_{\int} \\
    %~ \quad & \mx{B}_{\int}^{1} \mx{C} \leq \vc{b}_{\int} \\
    %~ \quad & [\vc{c}_0\tra, \vcd{c}_0\tra]\tra = \vc{x}_0 \\
    %~ \quad & \vc{c}_T = \vc{c}_T^{input} \\
\end{aligned} \end{equation}
\adnote{Did you really use w as a variable of your problem? Or do you compute it inside your constraint function as a function of the CoM pos and acc? And what about dL? It appears in the definition of w but then it is no longer there in the problem definition!}
The cost function $\ell$ is a weighted sum of the angular momentum and center-of-mass acceleration variation over the whole trajectory. 
The system dynamics $dyn$ tie together the position, velocity and acceleration of the center of mass. 
$\mathbf{Y}_u$ and $\mathbf{y}_u$ denote stacked kinematic constraints on the center of mass position, determined by the active contact locations.
The inequalities for each contact are determined in the same way that the reachable workspace is computed in Appendix~\ref{app:rom}, with
the effector serving as root. % (a triangulated object is a polytope, and as such can be described as a set of linear inequalities).

>>>>

\begin{equation} \label{eq:qp_rob} \begin{aligned}
%~ \find \quad & \mx{R} \in \Rv{3\times T}, \mxdd{C} \in  \Rv{6\times T} \\
%~ \minimize_{\mathbf{c}(t), \mathbf{\dot{c}}(t), \mathbf{\ddot{c}}(t), \mathbf{w}(t)}  \quad & \sum_{u=0}^{2} \int_{t_u}^{t_u + \Delta t_u}  \ell(\mathbf{c}(t), \mathbf{\dot{c}}(t), \mathbf{\ddot{c}}(t), \mathbf{w}(t)) \text{dt}  \\
\minimize_{\mathbf{\ddot{c}}(t), \dot{L}(t)}  \quad & \sum_{u=0}^{2} \int_{t_u}^{t_u + \Delta t_u}  \ell(\mathbf{\ddot{c}}(t), \dot{L}(t)) \text{dt}  \\
%~ \st \quad & \mathbf{\ddot{c}}(t) = dyn(\mathbf{c}(t), \mathbf{\dot{c}}(t), \mathbf{w}(t)) \\
%~ \st \quad & \mathbf{c}(t) =  dyn(\mathbf{\ddot{c}}, \mathbf{c}_{\mathbf{q}_0} )  \\
\st \quad & \mathbf{A}_u \mathbf{w}(t)  \leq \mathbf{b}_u , \forall t \in  \left[t_u, t_u + \Delta t_u \right[, \forall u \\
	\quad & \mathbf{Y}_u \mathbf{c}(t)  \leq \mathbf{y}_u , \forall t \in  \left[t_u, t_u + \Delta t_u \right[, \forall u \\
	\quad & \mathbf{c}(0)  = \mathbf{c}_{\mathbf{q}_0} \\
	\quad & \mathbf{c}(T)  = \mathbf{c}_{\mathbf{q}_1} \\
	\quad & \mathbf{c}(0)  = \mathbf{\dot{c}}(0)  = \mathbf{\ddot{c}}(0) = \mathbf{0}\\
	\quad & \mathbf{c}(T)  = \mathbf{\dot{c}}(T)  = \mathbf{\ddot{c}}(T) = \mathbf{0}\\
    %~ \quad & ({\vct{r}}\tra\vct{r}=1,  \forall t  ?) \\
    %~ \quad & \delta t \sum\limits_1^{T-1}{\vc{r}^1}\tra {\vc{r}^1} \ge t_{transit} \\
    %~ \quad & \mx{A}_{\int} \mxdd{C} \leq \vc{a}_{\int} \\
    %~ \quad & \mx{V}_{\int} \mxd{C} \leq \vc{v}_{\int} \\
    %~ \quad & \mx{B}_{\int}^{1} \mx{C} \leq \vc{b}_{\int} \\
    %~ \quad & [\vc{c}_0\tra, \vcd{c}_0\tra]\tra = \vc{x}_0 \\
    %~ \quad & \vc{c}_T = \vc{c}_T^{input} \\
\end{aligned} \end{equation}
%~ \adnote{Did you really use w as a variable of your problem? Or do you compute it inside your constraint function as a function of the CoM pos and acc? And what about dL? It appears in the definition of w but then it is no longer there in the problem definition!}
The cost function $\ell$ is a weighted sum of the angular momentum and center-of-mass acceleration variation over the whole trajectory.
The center-of-mass positions and velocities $\mathbf{c}(t)$, $\mathbf{\dot{c}}(t)$ are interval variables, obtained through the double integration of $\mathbf{\ddot{c}}(t)$.
Then $\mathbf{w}(t)$ is obtained directly from these variables. $\mathbf{c}_{\mathbf{q}_0}$ and $\mathbf{c}_{\mathbf{q}_1}$ are the center-of-mass positions for configurations
 $\mathbf{q}_0$ and $\mathbf{q}_1$ respectively.
%~ The system dynamics $dyn$ tie together the position, velocity and acceleration of the center of mass. 
$\mathbf{Y}_u$ and $\mathbf{y}_u$ denote stacked kinematic constraints on the center of mass position, determined by the active contact locations.
The inequalities for each contact are determined in the same way that the reachable workspace is computed in Appendix~\ref{app:rom}, with
the effector serving as root. % (a triangulated object is a polytope, and as such can be described as a set of linear inequalities).

### 2017-10-02 body/results.tex
andrea s comments

% !TEX root =  ../main_tro.tex
\section{Results}
\label{sec:results}
In this section we present some of the results obtained with our planner. The complete sequences are shown in the companion video.
Specifically, we demonstrate the planner for two legged robots, in a large variety of environments: the humanoid HRP-2 and the quadruped HyQ.
Finally, a last example suggests possible applications to dexterous manipulation.

At the end of the video, we validate our contact plans by exhibiting a solution to the interpolation problem $\mathcal{P}_3$.

@@

@@

\subsubsection{Choosing the scaling factor $s$} \label{sec:params}
%~ \deladp{To find a convenient value $s^*$ of $s$, we proceeded as follows. }
For several values of $s$, we generated $10 000$ configurations. 
%~ We then computed the sensitivity of the reachability condition (percentage of configurations in $C_{Reach}^0$ belonging to \gls{$C_{Contact}^0$}).
%~ Similarly we computed the specificity of the condition (percentage of configurations \textbf{not} in $C_{Reach}^0$ \textbf{not} belonging to \gls{$C_{Contact}^0$}).
We then computed to sensitivity and specificity of the reachability condition.  In this context, the sensitivity refers to the percentage of configurations in $C_{Reach}^0$, effectively belonging to \gls{$C_{Contact}^0$}. If a sampled configuration is in $C_{Reach}^0$, but our method is unable to generate a contact configuration from it, as a result the sensitivity
decreases. The sensitivity thus illustrates the confidence we have that any configuration in $C_{Reach}^0$ will effectively lead to a contact configuration.
Conversely, the specificity refers to the percentage of configurations \textbf{not} in $C_{Reach}^0$, effectively \textbf{not} belonging to \gls{$C_{Contact}^0$}.
If a sampled configuration is \textbf{not} in $C_{Reach}^0$, but our method is able to generate a contact configuration from it, as a result the specificity
decreases. The specificity thus illustrates the confidence we have that all configurations that allow contact creation belong to in $C_{Reach}^0$ (or informally, the confidence that we are not missing too many valid solutions).
We thus look for a compromise between sensitivity and specificity.

@@

\subsection{Validation of the contact plans} \label{sec:valid}
\adnote{I added the description of the simulations here, but I wonder whether this part should not be moved to the beginning of the Results section.}
To generate continuous movements from our contact plans we used either the framework proposed in \cite{Carpentier2016}, or our own implementation of a $\mathcal{P}_3$ solver (Appendix~\ref{app:optim}).
The resulting movements have been validated either on the real HRP-2 robot (details can be found in~\cite{Carpentier2016}), or with our dynamic simulator, based on a state-of-the-art algorithm~\cite{Kaufman2008}.
In the simulations we controlled the robot with a standard inverse-dynamics controller~\cite{DelPrete2015b}.
This controller tries to follow the given whole-body trajectories, giving higher priority to the center-of-mass and end-effectors tracking with respect to the joint tracking.
The controller also makes sure that the resulting contact forces lie inside the specified friction cones (we used a friction coefficient of 0.3), and that the joint position, velocity and torque limits are satisfied.
The companion video shows the obtained motions.

>>>>

% !TEX root =  ../main_tro.tex
\section{Results}
\label{sec:results}
In this section we present some of the results obtained with our planner. The complete sequences are shown in the companion video.
Specifically, we demonstrate the planner for two legged robots, in a large variety of environments: the humanoid HRP-2 and the quadruped HyQ.
%~ Finally, a last example suggests possible applications to dexterous manipulation.

Our contact plans are then interpolated with a dedicated solution to the interpolation problem $\mathcal{P}_3$. This allows us to validate the obtained
motions in a dynamic simulator. This validation is an important contribution as it increases the confidence that the contact plans we compute can effectively
result in feasible motions on the real robot. One motion is demonstrated on the real HRP-2 robot.
%~ The obtained motions can be seen at at the end of the video.

@@

\subsection{Experimental validation of the contact plans} \label{sec:valid}
%~ \adnote{I added the description of the simulations here, but I wonder whether this part should not be moved to the beginning of the Results section.}
To generate continuous movements from our contact plans we used either the framework proposed in \cite{Carpentier2016}, or our own implementation of a $\mathcal{P}_3$ solver (Appendix~\ref{app:optim}).
The resulting movements have been validated either on the real HRP-2 robot (details can be found in~\cite{Carpentier2016}), or with our dynamic simulator, based on a state-of-the-art algorithm~\cite{Kaufman2008}.
In the simulations we controlled the robot with a standard inverse-dynamics controller~\cite{DelPrete2015b}.
This controller tries to follow the given whole-body trajectories, giving higher priority to the center-of-mass and end-effectors tracking with respect to the joint tracking.
The controller also makes sure that the resulting contact forces lie inside the specified friction cones (we used a friction coefficient of 0.3), and that the joint position, velocity and torque limits are satisfied.
The companion video shows the obtained motions.

@@

\subsubsection{Choosing the scaling factor $s$} \label{sec:params}
%~ \deladp{To find a convenient value $s^*$ of $s$, we proceeded as follows. }
For several values of $s$, we generated $10 000$ configurations. 
%~ We then computed the sensitivity of the reachability condition (percentage of configurations in $C_{Reach}^0$ belonging to \gls{$C_{Contact}^0$}).
%~ Similarly we computed the specificity of the condition (percentage of configurations \textbf{not} in $C_{Reach}^0$ \textbf{not} belonging to \gls{$C_{Contact}^0$}).
We then computed the sensitivity and specificity of the reachability condition.  In this context, the sensitivity refers to the percentage of configurations in $C_{Reach}^0$, effectively belonging to \gls{$C_{Contact}^0$}. If a sampled configuration is in $C_{Reach}^0$, but our method is unable to generate a contact configuration from it, as a result the sensitivity
decreases. The sensitivity thus illustrates the confidence we have that any configuration in $C_{Reach}^0$ will effectively lead to a contact configuration.
Conversely, the specificity refers to the percentage of configurations \textbf{not} in $C_{Reach}^0$, effectively \textbf{not} belonging to \gls{$C_{Contact}^0$}.
If a sampled configuration is \textbf{not} in $C_{Reach}^0$, but our method is able to generate a contact configuration from it, as a result the specificity
decreases. The specificity thus illustrates the confidence we have that all configurations that allow contact creation belong to $C_{Reach}^0$ (or informally, the confidence that we are not missing valid solutions).
We thus look for a compromise between sensitivity and specificity.

@@
